A Proposal for the Use of Backtranslation to Decode Whale Songs

### 2024-07-01 tex/paper.tex
some improved wording

\section{Introduction}
Decoding whale songs presents a unique challenge in the field of animal communication. In this paper, I propose an unsupervised translation approach motivated by understanding animal communication. This involves using backtranslation techniques to create a model that can translate whale vocalizations into English and back, ensuring that the translations are contextually and semantically accurate.\\ \\
I will use the term "Whale" to refer to the language Whales are speaking. For example, "she understands both Whale and English."

>>>>

\section{Introduction}
Decoding whale songs presents a unique challenge in the field of animal communication. I believe communication with whales will both teach us for the first time a complete language of another species, as well as enable communication with many more animals. This will be critical to both understand the desires and steward the environment for these animals, as well as raise popular awareness of how humanity is affecting wild animals on this planet.\\
In this paper, I propose an unsupervised translation approach motivated by understanding animal communication. This involves using backtranslation techniques to create a model that can translate whale vocalizations into English and back, ensuring that the translations are contextually and semantically accurate.\\ \\
I will use the term "Whale" to refer to the language Whales are speaking. For example, "she understands both Whale and English."
